A pair of co-moving, Sun-like stars with different chemical abundances:\\ a possible signature of copious rocky accretion (needs work)

### 2017-05-01 paper/ms.tex
more on ages

Surface lithium abundance in a sun-like star such as \sunanalog\ decreases with its age
due to mixing induced by convection or rotation which brings lithium
into the interior ($T>2.5 \times 10^{6}$~K)
where it will be destroyed by proton capture burning.
Thus, surface lithium abundance is an indicator of stellar ages.
The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
according to the theoretical models tuned to explain the solar lithium abundance
and rotational profile (\citealt{2005Sci...309.2189C}).
The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
showing the largest difference among all measured elements.
This translates to $\sim 500$~Myr difference in age.
Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
it is unclear, however, whether this higher $\elem{Li}$ abundance
means a younger age or something else.
For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
to the engulfment of substellar companions such as gas giant planets or brown dwarfs
which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).
We come back to the $\elem{Li}$ difference later in our discussion.

>>>>

Surface lithium abundance in a sun-like star such as \sunanalog\ decreases with its age
due to mixing induced by convection or rotation which brings lithium
into the interior ($T>2.5 \times 10^{6}$~K)
where it will be destroyed by proton capture burning.
Thus, surface lithium abundance is an indicator of stellar ages.
The $\elem{Li}$ abundance of $2.25$ for \sunanalog\ implies an age of $\lesssim 1$~Gyr
according to the theoretical models tuned to explain the solar lithium abundance
and rotational profile (\citealt{2005Sci...309.2189C}).
The lithium abundance of \bizarreone\ is still higher by $0.5$~dex
showing the largest difference among all measured elements.
This translates to $\sim 500$~Myr difference in age.
Given the overall higher metal abundances and the peculiar abundance patterns in \bizarreone,
it is unclear, however, whether this higher $\elem{Li}$ abundance
means a younger age or something else.
For example, the presence of $\elem{Li}$-rich red giant stars has been attributed
to the engulfment of substellar companions such as gas giant planets or brown dwarfs
which may replenish $\elem{Li}$ (\citealt{Casey:2016aa}).

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{isochrones.png}
  \caption{Isochrone ages of \sunanalog\ and \bizarreone.
    On the left, we show the two stars on $T_\mathrm{eff}-\log(g)$ plane,
    and on the right, the color-magnitude diagram using \gaia\ $G$ band
    and \tmass\ $J$ band magnitudes.
    In each panel, \project{MIST} isochrones (\citealt{Choi:2016aa}) at $28$~Myr and $2$~Gyr are
    plotted. The thicker and thinner lines are for $\feh = 0.$ and $0.2$,
    corresponding to values of \sunanalog\ and \bizarreone.
  }
  \label{fig:isochrones}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{sed.png}
  \caption{Spectral energy distributions (SEDs) of \sunanalog\ and \bizarreone.
    The yellow line is the SED of a blackbody at $T=5878$ scaled arbitrarily.
  }
  \label{fig:sed}
\end{figure}

Given the precise measurements of $\log(g)$ and $T_\mathrm{eff}$,
comparing these values to theoretical isochrones may also be indicative of the two stars' ages.
We compared the measured $\log(g)$ and $T_\mathrm{eff}$ to \project{MIST} isochrones at two
different $\feh$ of $0$ and $0.2$, corresponding to the $\feh$ of \sunanalog\ and \bizarreone.
The two most consistent isochrones at $28$~Myr and $2$~Gyr based on $\chi^2$ values
are plotted in Figure~\ref{fig:isochrones}.
For \sunanalog\ ($\feh = 0.01$), the most consistent isochrone is that for
an age of $2$~Gyr and $\feh = 0.2$.
The $\log(g)$ values of the two stars, especially of \bizarreone\, seem to suggest
that they could be at the end of the pre-main sequence phase.
However, an age of $28$~Myr for \sunanalog\ is in tension with the larger age ($800$~Myr)
inferred from its $\elem{Li}$ abundance.
Also, at such a young age, we may expect to see infrared excess from a circumstellar disk or
X-ray emission from magnetic activity. 
However, the spectral energy distributions of the two stars based on
\project{Tycho-2}, \tmass, \project{WISE} photometry (\todo{CITE}) are consistent with blackbody,
and no relatable X-ray point sources are found in the \project{ROSAT} All-Sky Survey
around the two stars,
On the other hand, the most consistent main sequence age ($2$~Gyr) also is in tension with
its relatively high $\elem{Li}$ abundance, not to mention with the $\log(g)$ of \bizarreone\
if the two stars should have the same age.
